### 2018-10-05 paper.tex
fist commit

\documentclass{sigplanconf}

\usepackage{graphicx}
\usepackage{url}
\usepackage{listings}
\usepackage{amsmath}
\usepackage[font={small}]{caption}

\newcommand{\dfn}[1]{\textit{#1}} % For initial definitions of terms

% For marking text we're probably dropping.
\newcommand{\ignore}[1]{}

% For marking text that we might like to include in a final draft, if
% accepted to RADIO, but that will not fit within the 5-page limit.
\newcommand{\saveforlater}[1]{}

% For marking important work items.
\newcommand{\todo}[1]{\textbf{TODO: #1}}

\lstset{ %
    captionpos=b,
    frame=single
}

\begin{document}

\title{ERSPAN Support for Linux}
\authorinfo{
  \(
  \begin{matrix}
    \textrm{Greg Rose} & \textrm{William Tu} \\
    \textrm{roseg@vmware.com} & \textrm{tuc@vmware.com} \\
  \end{matrix}
  \)
}
{}{}

\maketitle

\begin{abstract}
Port mirroring is one of the most common network troubleshooting techniques.
SPAN (Switch Port Analyzer) allows a user to send a copy of the monitored traffic
to a local or remote device using a sniffer or packet analyzer.
RSPAN is similar, but sends and received traffic on a VLAN. ERSPAN extends the
port mirroring capability from Layer 2 to Layer 3, allowing the mirrored traffic
to be encapsulated in an extension of the GRE (Generic Routing Encapsulation) protocol
and sent through an IP network.  In addition, ERSPAN carries configurable metadatas
(e.g., session ID, timestamps), so that the packet analyzer has better understanding
of the packets.

ERSPAN for IPv4 was added into Linux kernel in 4.14, and for IPv6 in 4.16.
The implementation includes both transmission and reception and is based on the
existing ip\_gre and ip6\_gre kernel module.  As a result, Linux today can act as
an ERSPAN traffic source sending the ERSPAN mirrored traffic to the remote host,
or an ERSPAN destination which receives and parses the ERSPAN packets generated
from Cisco or other ERSPAN-capable switches.

We’ve added both the native tunnel support and metadata-mode tunnel support.
In this paper, we demonstrate three ways to use the ERSPAN protocol.
First, for Linux users, using iproute2 to create native tunnel net device.
Traffic sent to the net device will be encapsulated with the protocol header
accordingly and traffic matching the protocol configuration will be received
from the net device.  Second, for eBPF users, using iproute2 to create metadata-mode
ERSPAN tunnel.  With eBPF TC hook and eBPF tunnel helper functions, users can
read/write ERSPAN protocol’s fields in finer granularity.
Finally, for Open vSwitch users, using the netlink interface to create a switch
and programmatically parse, lookup, and forward the ERSPAN packets based on flows
installed from the userspace.

\end{abstract}

\section{Introduction}\label{introduction}

\end{document}

### 2018-10-08 paper.tex
add introduction

@@
 \begin{abstract}
+Port mirroring is one of the most common network troubleshooting techiques.
+Switch Port Analyzer, SPAN, allows a user to send a copy of the monitored traffic
+to a local or remote device using a sniffer or packet analyzer.
+Encapsulated Remote SPAN, ERSPAN, extends the basic port mirroring capability
+from Layer 2 to Layer 3, allowing the mirrored traffic to be sent through an IP network.
+
+ERSPAN was added to Linux kernel in 4.14 for IPv4 and 4.16 for IPv6.
+In this paper, we demonstrate three ways to use the ERSPAN protocol.
+First, using iproute2 to create native tunnel net device.
+Traffic sent to the net device will be encapsulated with the protocol header
+accordingly and traffic matching the protocol configuration will be received
+from the net device.  Second, for eBPF users, using iproute2 to create metadata-mode
+ERSPAN tunnel and attach the tunnel metadata implementation in eBPF code.
+Finally, Open vSwitch users can use netlink interface to create a switch
+and programmatically parse, lookup, and forward the ERSPAN packets based on flows
+installed from the userspace.
+
+\end{abstract}
+
+\section{Introduction}\label{introduction}
 Port mirroring is one of the most common network troubleshooting techniques.
@@
 
-We’ve added both the native tunnel support and metadata-mode tunnel support.
-In this paper, we demonstrate three ways to use the ERSPAN protocol.
+We have added both the native tunnel support and metadata-mode tunnel support.
+we demonstrate three ways to use the ERSPAN protocol.
 First, for Linux users, using iproute2 to create native tunnel net device.
@@
 
-\end{abstract}
+\begin{figure}
+{\scriptsize
+\begin{verbatim}
+                             Linux                    Linux
++----------+         +-------------------+      +---------------+
+| Physical |         |     VM1  VM2 ...  |      |     linux     |
+| Machines |         |      |    |       |      |    netdevs    |
++----------+         |  +--------------+ |      |      |        |
+    | links          |  | Open vSwitch | |      | ERSPAN        |
+    |                |  +--------------+ |      | netdev        |
++------------+       +-------||----------+      +-||------------+ 
+|Cisco switch|               ||                   ||
++------------+               || ERSPAN            || ERSPAN
+   || ERSPAN tunnel          || tunnel            || tunnel
+   ||                        ||                   ||
+    /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\     +-------+ 
+    {       Layer 3 IPv4, Ipv6 network             } === |Traffic|
+    \~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~/     |Sniffer|
+                                                         +-------+
+\end{verbatim}   
+}
+\vspace{-0.5em}
+\caption{Overview of the ERSPAN tunnel use cases. ERSPAN tunnel can be
+created between }
+\label{overview}
+\vspace{-1.0em}
+\end{figure}
 
-\section{Introduction}\label{introduction}
+ERSPAN is popular in the followin use cases~\ref{erspanietf}:
+\begin{itemize}
+\item Debugging network issues by tracking the control and data frames. 
+\item Monitoring Voice-over-IP, VoIP, packets for delay and jitter analysis
+\item Monitoring network transactions for latency analysis
+\item Monitoring network traffic for anomaly detection
+\end{itemize}
+Figure~\ref{fig:overview} shows an example setup of ERSPAN tunnels.
+A network administrator first sets up multiple source network devices
+and filters the interested portion of the traffic he/she wants
+to inspect.  One case on the left-most is to create the ERSPAN tunnel
+between the Cisco switch and a traffic sniffer.  Depending on the
+features in the Cisco switch, different filters can be applied to the
+traffic.  In the middle of the figure, for multiple virtual machines running
+inside a Linux box, the virtual switch forwarding the packet between
+virtual and physical network can also create ERSPAN tunnels between
+the software switch and remote traffic sniffer.
+Here, Open vSwitch~\cite{ovs} is an example capabale of creating filters
+and forward packets to ERSPAN tunnels. More detailed configurations of
+Open vSwitch is described in later section.
 
+The ERSPAN tunnel is represented in Linux as a netdev and configured
+through iproute2~\cite{iproute2}. Any packet that is placed into its send
+queue will be encapsulated based on the netdev's ERSPAN configuration.  
+As a result on the right-most, any other linux netdev which wants to create
+a ERSPAN mirrored packet simply make a copy and forward to the ERSPAN netdev.
+For example, a physical netdev can use TC~\cite{tc} to copy a packet
+to the erspan tunnel~\cite{tcselftest}.
+
+Mirrored traffic arrives at the sniffer machine needs to be able to
+extract and restore the original monitored frame.
+For Linux user, an ERSPAN tunnel can also be used at the sniffer size.
+Any packet arriving at the ERSPAN tunnel netdev's receive queue will
+be decapsulated. Tools such as Wireshark~\cite{wireshark} can be used
+to inspect the mirrored packet.
+
+\section{ERSPAN Protocol}
+ERSPAN protocol was developed by Cisco and its specification is published at IETF
+draft~\cite{erspan}.  
+Figure~\ref{fig:erspanhdr} shows an example of ERSPAN encapsulated
+packet, with outer header consists of Ethernet header, followed by IPv4/IPv6
+header, followed by a fixed 8-byte GRE header, and followed by ERSPAN header.
+After the ERSPAN header, the inner frame is followed so that the ERSPAN receiver
+or packet sniffer can extract the original frame.
+The use of the IP protocol as part of the outer header is important because it
+makes the mirrored traffic routable across any IP network.
+
+ERSPAN protocol has two versions; version 1 (type II) and
+version 2 (type III). ERSPAN protocol is layered on top of the GRE (Generic Routing
+Encapsulation) protocol, with GRE's sequence number enabled.  For ERSPAN type II,
+the GRE's next protocol type is 0x88BE with 8-byte ERSPAN header size, and for
+ERSPAN type III, the GRE's next protocol type is 0x22EB with 12-byte ERSPAN header
+size, if no optinal subheader enabled.
+The following subsection describes the two ERSPAN header formats.
+
+\begin{figure}
+{\scriptsize
+\begin{verbatim}
+<------------ outer -------------->  <---- inner ----...
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+| Ether |  IP  |  GRE  |  ERSPAN  | Ether |  IP  | ...   
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+\end{verbatim}
+}
+\vspace{-1.0em}
+\caption{An example of mirrored packet with outer header containing
+the GRE and ERSPAN header, followed by the innter Ethernet frame.}
+\label{erspanhrd}
+\vspace{-1.0em}
+\end{figure}
+
+\subsection{GRE header}
+{\scriptsize
+\begin{verbatim}
+GRE header for ERSPAN encapsulation (8 octets [34:41]) -- 8 bytes
+0                   1                   2                   3
+0 1 2 3 4 5 6 7 8 9 0 1 2 3 4 5 6 7 8 9 0 1 2 3 4 5 6 7 8 9 0 1
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+|0|0|0|1|0|00000|000000000|00000|    Protocol Type for ERSPAN   |
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+|      Sequence Number (increments per packet per session)      |
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+\end{verbatim}
+}
+Note that in the above GRE header [RFC1701] out of the C, R, K, S,
+s, Recur, Flags, Version fields only S (bit 03) is set to 1. The
+other fields are set to zero, so only a sequence number follows.
+
+Sequence number is useful in many cases that
+when the mirrored traffic is re-ordered.
+
+\subsection{ERSPAN Type II}
+ERSPAN type II has 8-byte feature header with the following format.
+{\scriptsize
+\begin{verbatim}
+ERSPAN Version 1 (Type II) header (8 octets [42:49])
+0                   1                   2                   3
+0 1 2 3 4 5 6 7 8 9 0 1 2 3 4 5 6 7 8 9 0 1 2 3 4 5 6 7 8 9 0 1
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+|  Ver  |          VLAN         | COS | En|T|    Session ID     |
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+|      Reserved         |                  Index                |
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+\end{verbatim}
+}
+
+The ERSPAN Type II encapsulation adds to the original
+frame a composite header comprising: 14 (802.3) + 20 (IP) + 8 (GRE)
+ + 8 (ERSPAN) octets, in addition to a trailing 4-octet Ethernet CRC.
+(Note that an 802.1Q encapsulation [802.1Q] would add 4 additional
+octets but not reduce the Ethernet MTU size of the container frame.
+
+VLAN riginal VLAN of the frame.
+
+COS
+Class of Service of the monitored frame.
+
+En
+The trunk encapsulation type associated with the ERSPAN source port for  ingress ERSPAN traffic.
+T
+Indicates that the frame copy encapsulated in the ERSPAN packet has been truncated
+Session ID
+Identification associated with each ERSPAN session
+Index
+Index associated with the ERSPAN traffic's source port and direction, this field is platform dependent.
+
+\subsection{ERSPAN Type III}
+{\scriptsize
+\begin{verbatim}
+ERSPAN Version 2 (Type III) header (12 octets [42:49])
+0                   1                   2                   3
+0 1 2 3 4 5 6 7 8 9 0 1 2 3 4 5 6 7 8 9 0 1 2 3 4 5 6 7 8 9 0 1
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+|  Ver  |          VLAN         | COS |BSO|T|     Session ID    |
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+|                          Timestamp                            |
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+|             SGT               |P|    FT   |   Hw ID   |D|Gra|O|
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+\end{verbatim}
+}
+
+Type III introduces a larger and more flexible composite header to
+support additional fields useful for applications such as network
+management, intrusion detection, performance and latency analysis
+etc. that require to know all the original parameters of the
+mirrored frame, including those not present in the original frame
+itself.
+
+The ERSPAN Type III composite header includes a mandatory 12-octet
+portion followed by an optional 8-octet platform specific sub-header
+
+ERSPAN Type III supports all of the ERSPAN type II features and
+functionality and adds these enhancements:
+Provides timestamp information in the ERSPAN Type III header that can
+be used to calculate packet latency among edge, aggregate, and core switches.
+Identifies possible traffic sources using the ERSPAN Type III header fields
+
+Provides the ability to configure timestamp granularity across all VDCs to
+determine how the clock manager synchronizes the ERSPAN timers
+
+\section{Implementation}
+The use of the IP protocol as part of the transport is critical to
+be able to carry the mirrored traffic across any IP-based network.
+The GRE component instead is particularly important to be able to
+piggyback different data formats along with the copy of the original
+frame.
+
+ERSPAN can carry either  
+ERSPAN for IPv4 was implemented under net/ipv4/ip\_gre.c and was
+upstreamed to Linux kernel in 4.14~\cite{erspanipv4}.
+The ERSPAN for IPv6
+
+\subsection{IPv4}
+
+gre: introduce native tunnel support for ERSPAN
+
+The ERSPAN implementation for IPV
+\subsection{IPv6}
+\subsection{Limitation}
+DF bit is set to prevent fragmentation
+• GRE Header protocol type of 0x88BE
+• PFC3 and above supports ERSPAN (sup720, sup32)
+• Cisco ASR supports ERSPAN as well
+• ERSPAN ID uniquely identifies source sessions
+
+%https://sharkfestus.wireshark.org/sharkfest.10/D-2_Chung%20A%20Variety%20of%20Ways%20to%20Capture%20and%20Analyze%20Packets.pdf
+
+\subsection{fragmentation}
+\section{Use Cases}
+Port mirroring and monitoring overview
+Port mirroring is a method of monitoring network traffic that forwards a copy of each incoming or outgoing packet from one port on a network switch to another port where the packet can be analyzed.
+Port mirroring can be used as a diagnostic tool or debugging feature, especially for preventing attacks.
+Port mirroring can be managed locally or remotely.
+You can configure port mirroring, by assigning a port (known as the Monitor port), from which the packets are copied and sent to a destination port (known as the Mirror port).
+All packets received on the Monitor port or issued from it, are forwarded to the second port.
+You next attach a protocol analyzer on the mirror port to monitor each segment separately.
+The analyzer captures and evaluates the data without affecting the client on the original port.
+
+\subsection{Linux iproute2}\label{iproute2}
+\subsection{eBPF}\label{ebpf}
+\subsection{Open vSwitch}\label{ovs}
+\subsection{Cisco Switch}
+    gre: introduce native tunnel support for ERSPAN
+
+\begin{verbatim}
+    monitor session 100 type erspan-source
+      erspan-id 123
+      vrf default
+      destination ip 172.16.1.200
+      source interface Ethernet1/11 both
+      source interface Ethernet1/12 both
+      no shut
+    monitor erspan origin ip-address 172.16.1.100 global
+\end{verbatim}
+
+\section{Conclusion}
+\section{Acknowledgments}
+\section{Future Work}
 \end{document}

### 2018-10-09 paper.tex
add prototol implementation

@@
   \begin{matrix}
-    \textrm{Greg Rose} & \textrm{William Tu} \\
-    \textrm{roseg@vmware.com} & \textrm{tuc@vmware.com} \\
+    \textrm{William Tu} & \textrm{Greg Rose} \\
+    \textrm{VMware Inc.} & \textrm{VMware Inc.} \\
+    \textrm{u9012063@gmail.com} & \textrm{gvrose8192@gmail.com} \\
   \end{matrix}
@@
 
-ERSPAN is popular in the followin use cases~\ref{erspanietf}:
+ERSPAN is popular in the followin use cases~\cite{erspan_ietf}:
 \begin{itemize}
@@
 \end{itemize}
-Figure~\ref{fig:overview} shows an example setup of ERSPAN tunnels.
+Figure~\ref{overview} shows an example setup of ERSPAN tunnels.
 A network administrator first sets up multiple source network devices
@@
 Mirrored traffic arrives at the sniffer machine needs to be able to
-extract and restore the original monitored frame.
+extract and restore the original monitored frame.  To differentiated
+the three use cases, the administrator can create three ERSPAN session
+ID, a configuration parameter for grouping the mirrored traffic.
 For Linux user, an ERSPAN tunnel can also be used at the sniffer size.
@@
 
-\section{ERSPAN Protocol}
+\section{ERSPAN Protocol Implementation}
+\begin{figure}
+{\scriptsize
+\begin{verbatim}
+<------------ outer -------------->  <---- inner ----...
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+| Ether |  IP  |  GRE  |  ERSPAN  | Ether |  IP  | ...   
++-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
+\end{verbatim}
+}
+\vspace{-1.0em}
+\caption{An example of mirrored packet with outer header containing
+the GRE and ERSPAN header, followed by the innter Ethernet frame.}
+\label{erspanhdr}
+\vspace{-1.0em}
+\end{figure}
+
 ERSPAN protocol was developed by Cisco and its specification is published at IETF
-draft~\cite{erspan}.  
-Figure~\ref{fig:erspanhdr} shows an example of ERSPAN encapsulated
+draft~\cite{erspan_ietf}. 
+Figure~\ref{erspanhdr} shows an example of ERSPAN encapsulated
 packet, with outer header consists of Ethernet header, followed by IPv4/IPv6
@@
 size, if no optinal subheader enabled.
-The following subsection describes the two ERSPAN header formats.
 
-\begin{figure}
-{\scriptsize
-\begin{verbatim}
-<------------ outer -------------->  <---- inner ----...
-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
-| Ether |  IP  |  GRE  |  ERSPAN  | Ether |  IP  | ...   
-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
-\end{verbatim}
-}
-\vspace{-1.0em}
-\caption{An example of mirrored packet with outer header containing
-the GRE and ERSPAN header, followed by the innter Ethernet frame.}
-\label{erspanhrd}
-\vspace{-1.0em}
-\end{figure}
+In this section we describe the basic ERSPAN protocol header format
+along with its implementation to Linux kernel.
+For IPv4/IPv6, the implementation is under net/ipv4/ip\_gre.c and
+net/ipv6/ip6\_gre.c. Also a userspace API header, include/uapi/linux/erspan.h
+is added for metadata-mode tunnel users.
 
-\subsection{GRE header}
+\subsection{Native v.s Metadata-Mode Tunnel}
+%https://netdevconf.org/1.2/papers/borkmann.pdf
+There are two tunnel type implementations in Linux kernel:
+native tunnel and metadata-mode tunnel~\cite{lwtunnel}.
+Native tunnel is the basic way of creating tunnels in Linux.
+A tunnel netdev is created with per tunnel-specific configuration,
+tied together with the netdev. For example, creating a GRE tunnel
+with key and sequence number can be done by:
+\texttt{ip link add dev gre123 type gretap local 1.1.1.1 remote 2.2.2.2 seq key 0xfb}.
+As a result, $N$ different tunnel configurations require creating
+$N$ number of netdevs.  In certain cases such as network virtualization,
+this is not scalable because every host in the network creates
+mutiple tunnels with different configurations to every other hosts~\cite{mvp}.
+
+Metada-mode tunnel, or light weight tunnel, is designed for solving
+the limitation.  The fundamental idea is that only one netdev per
+tunnel type is required to represent multiple tunnels.
+This means that the tunnel configuration of a particular type
+of the tunnel must be passed to the tunnel netdev in order
+to encapsulate the packet.  For example, creating a metadata-mode
+tunnel can be done by:
+\texttt{ip link add dev type gretap external}.
+Note that there is no configuration parameters assigned at device creation
+time. The tunnel configuration is set-up per-packet at run-time.
+Currently there are two ways of using metadata-mode tunnel, one through
+OVS and the other through eBPF~\cite{dborkman}.
+We implement both the native mode and metadata-mode~\cite{erspanmd}
+for ERSPAN type II and type III.
+More examples of using native and metadata-mode tunnel are upstreamed
+under tools/testing/selftest/bpf/\{test\_tunnel.sh, test\_tunnel\_kern.c\}.
+
+\subsection{GRE}
+ERSPAN follows a fixed 8-byte GRE header with the below value.
 {\scriptsize
@@
 }
-Note that in the above GRE header [RFC1701] out of the C, R, K, S,
-s, Recur, Flags, Version fields only S (bit 03) is set to 1. The
-other fields are set to zero, so only a sequence number follows.
+Note that only the sequence number bit in the FLAGS fields is set.
+Sequence number is useful at the snifffer site where the mirrored
+traffic arrives out-of-the-order.  Depending on the protocol type,
+ERSPAN type II or type III is followed next.
+% note: we do not implement per session seq number?
 
-Sequence number is useful in many cases that
-when the mirrored traffic is re-ordered.
+\textbf{Implementation: }
+%commit: gre: add sequence number for collect md mode.
+Before introducing ERSPAN, Linux kernel already supports IPv4 GRE native
+and metadata mode.  So our effort is to purely add ERSPAN implementation
+on top of existing GRE code base~\cite{erspantype2}.
+One minor limitation is that existing metadata-mode does not support
+GRE sequence number, we've upstreamed the implementation~\cite{greseq}.
+
+For IPv6, there is no metadata mode feature before 4.16.
+We first implemented the metadata-mode support for IPv6 GRE~\cite{ip6md},
+then upstreamed the ERSPAN feature~\cite{ip6erspanmd, ip6erspan}.
+%commit 6712abc168ebac90b46 ip6_gre: add ip6 gre and gretap collect_md mode
 
@@
 }
+The ERSPAN Type II encapsulation adds to the original
+frame a composite header comprising: 14-byte (802.3) + 20-byte (IP)
++ 8-byte (GRE)  + 8-byte (ERSPAN), in addition to a trailing 4-byte
+Ethernet CRC.
+The VLAN field shows the original VLAN of the frame, the COS means
+Class of Service of the monitored frame.
+En field shows the trunk encapsulation type associated with the ERSPAN
+source port.
+When the mirrored frame is truncated, T bit is set to indicate the
+frame has been truncated.
+Session ID is a 10-bit field as an identification of each ERSPAN mirring
+session.
+Index is a platform-depedent field for specifying port number and direction.
 
-The ERSPAN Type II encapsulation adds to the original
-frame a composite header comprising: 14 (802.3) + 20 (IP) + 8 (GRE)
- + 8 (ERSPAN) octets, in addition to a trailing 4-octet Ethernet CRC.
-(Note that an 802.1Q encapsulation [802.1Q] would add 4 additional
-octets but not reduce the Ethernet MTU size of the container frame.
-
-VLAN riginal VLAN of the frame.
-
-COS
-Class of Service of the monitored frame.
-
-En
-The trunk encapsulation type associated with the ERSPAN source port for  ingress ERSPAN traffic.
-T
-Indicates that the frame copy encapsulated in the ERSPAN packet has been truncated
-Session ID
-Identification associated with each ERSPAN session
-Index
-Index associated with the ERSPAN traffic's source port and direction, this field is platform dependent.
+%\noindent
+\textbf{Implementation: }
+Type II introduces two new configurable fields to netlink API;
+the Session ID and Index.
+Session ID is configured by users through iproute2 tool with netlink API. 
+Since ERSPAN does not use the GRE Key field, we re-use the
+\texttt{IFLA\_GRE\_IKEY, IFLA\_GRE\_OKEY} as the session ID field.
+Index is also configurable by users through iproute2.
+The COS field and VLAN field are extrated from the original frame and set
+properly.  The truncate bit is detected by comparing the the mirrored frame's
+skb->len and the length its IP header reports~\cite{erspantruncate}.
+%commit: erspan: auto detect truncated packets.
 
 \subsection{ERSPAN Type III}
+ERSPAN type III has 12-byte feature header with the following format.
 {\scriptsize
@@
 }
+Type III introduces more flexible composite header to support additional
+fields.  BSO, Bad/Short/Oversized, allows the sniffer to identify whether
+the frame payload has CRC error, too short, or too large~\cite{bso}.
+Timestamp is a 4-byte fields and can be configured with different granularities
+(100 microseconds, 100 nanosecond, or IEEE1588) at the Gra field.
+SGT stands for security group tag of the monitored frame, P field
+indicates that the ERSPAN payload is an Ethernet protocol frame.
+FT,Frame Type, indicates whether the mirrored frame is a Ethernet
+802.3 frame, or a IP packet.
+Hardware ID, Hw ID, is an unique identifier of an ERSPAN engine
+Direction bit, D, indicates whether the original frame was
+SPAN'ed in ingress(0) or in egress(1).
+Finally, O indicates whether or not the optinal platform-specific
+subheader is presented.
 
-Type III introduces a larger and more flexible composite header to
-support additional fields useful for applications such as network
-management, intrusion detection, performance and latency analysis
-etc. that require to know all the original parameters of the
-mirrored frame, including those not present in the original frame
-itself.
+\textbf{Implementation: }
+For type III, we introduced another two fields to kernel through
+netlink API; hardware ID and direction.
+The COS, BSO, and T fields can be extracted or inferred from the mirrored
+frame. Timestamp value is calculated by calling the kernel
+\texttt{ktime\_get\_real()} with 100 microseconds granularity.
+Currently we do not support other timer granulartiy.
+In addition, the SGT is hard-coded to 0, non-ethernet mirrored packet
+is not supported, so FT is always 0 and P is set to 1.
+There is no implementation of sub-headers, so O bit is 0.
 
-The ERSPAN Type III composite header includes a mandatory 12-octet
-portion followed by an optional 8-octet platform specific sub-header
-
-ERSPAN Type III supports all of the ERSPAN type II features and
-functionality and adds these enhancements:
-Provides timestamp information in the ERSPAN Type III header that can
-be used to calculate packet latency among edge, aggregate, and core switches.
-Identifies possible traffic sources using the ERSPAN Type III header fields
-
-Provides the ability to configure timestamp granularity across all VDCs to
-determine how the clock manager synchronizes the ERSPAN timers
-
-\section{Implementation}
-The use of the IP protocol as part of the transport is critical to
-be able to carry the mirrored traffic across any IP-based network.
-The GRE component instead is particularly important to be able to
-piggyback different data formats along with the copy of the original
-frame.
-
-ERSPAN can carry either  
+\section{Use Cases}
 ERSPAN for IPv4 was implemented under net/ipv4/ip\_gre.c and was
@@
 \section{Future Work}
+
+\bibliography{paper.bib}                                                                                                   
+\bibliographystyle{plain}
+
 \end{document}

### 2018-10-09 paper.tex
add example

@@
 \usepackage[font={small}]{caption}
-
+\newcommand{\mycomment}[1]{}
 \newcommand{\dfn}[1]{\textit{#1}} % For initial definitions of terms
@@
 
-\section{Use Cases}
-ERSPAN for IPv4 was implemented under net/ipv4/ip\_gre.c and was
-upstreamed to Linux kernel in 4.14~\cite{erspanipv4}.
-The ERSPAN for IPv6
+\section{Example Use Case}
+\begin{figure}
+{\scriptsize
+\begin{verbatim}
+ session 10            Linux, session 20        Linux, session 30
++----------+         +-------------------+      +----------------+
+| Physical |         |     VM1  VM2 ...  |      |     linux      |
+| Machines |         | 10.1.1.3  |       |      |    netdevs     |
++----------+         |  +--------------+ |      |      |         |
+    | links          |  | Open vSwitch | |      | ERSPAN 10.1.1.4|
+    | 10.1.1.2       |  +--------------+ |      | netdev         |
++------------+       +-------||----------+      +-||------------+ 
+|Cisco switch|               ||                   ||
++------------+               || ERSPAN            || ERSPAN
+   || ERSPAN tunnel          || tunnel            || tunnel
+   || (192.168.1.2)          || (192.168.1.3)     || (192.168.1.4)
+    /~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~\     +-------+ 
+    {       Layer 3 IPv4, Ipv6 network             } === |Traffic|
+    \~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~~/     |Sniffer|
+                192.168.1.*                              +-------+
+                                                        192.168.1.1
+\end{verbatim}   
+}
+\vspace{-0.5em}
+\caption{Example of creating three ERSPAN monitoring sessions, $10, 20, 30$,
+in a $10.1.1.*$ internal network, mirroring traffic over a $192.168.1.*$ IP network.}
+\label{example}
+\vspace{-1.0em}
+\end{figure}
 
-\subsection{IPv4}
+We use Figure~\ref{example} as an example topology to demostrate
+the three configuration ways of ERSPAN.
+Assuming a network administrator wants to monitor a network consists
+of 1) physical machines connected to Cisco switches, 2)
+virtualized Linux machine with multiple VMs deployed and virtual switch
+(openvswitch.ko) enforcing the fowarding policies, and
+3) non-virtualized Linux physical machines, e.g., service nodes
+in data center such as gateways.
+Assuming all the monitored servers are under IP subnet of $10.1.1.*$,
+and We place a traffic sniifer over another IP network of $192.168.1.*$.
+The following subsection describes the configuration for each case.
 
-gre: introduce native tunnel support for ERSPAN
-
-The ERSPAN implementation for IPV
-\subsection{IPv6}
-\subsection{Limitation}
-DF bit is set to prevent fragmentation
-• GRE Header protocol type of 0x88BE
-• PFC3 and above supports ERSPAN (sup720, sup32)
-• Cisco ASR supports ERSPAN as well
-• ERSPAN ID uniquely identifies source sessions
-
-%https://sharkfestus.wireshark.org/sharkfest.10/D-2_Chung%20A%20Variety%20of%20Ways%20to%20Capture%20and%20Analyze%20Packets.pdf
-
-\subsection{fragmentation}
-\section{Use Cases}
-Port mirroring and monitoring overview
-Port mirroring is a method of monitoring network traffic that forwards a copy of each incoming or outgoing packet from one port on a network switch to another port where the packet can be analyzed.
-Port mirroring can be used as a diagnostic tool or debugging feature, especially for preventing attacks.
-Port mirroring can be managed locally or remotely.
-You can configure port mirroring, by assigning a port (known as the Monitor port), from which the packets are copied and sent to a destination port (known as the Mirror port).
-All packets received on the Monitor port or issued from it, are forwarded to the second port.
-You next attach a protocol analyzer on the mirror port to monitor each segment separately.
-The analyzer captures and evaluates the data without affecting the client on the original port.
-
-\subsection{Linux iproute2}\label{iproute2}
-\subsection{eBPF}\label{ebpf}
-\subsection{Open vSwitch}\label{ovs}
 \subsection{Cisco Switch}
-    gre: introduce native tunnel support for ERSPAN
-
+We use Nexus 5000 switch and configure its ERSPAN tunnel
+on ports 11 and 12 as below.
 \begin{verbatim}
-    monitor session 100 type erspan-source
-      erspan-id 123
+    monitor session 10 type erspan-source
+      erspan-id 10
       vrf default
-      destination ip 172.16.1.200
+      destination ip 192.168.1.1
       source interface Ethernet1/11 both
@@
       no shut
-    monitor erspan origin ip-address 172.16.1.100 global
+    monitor erspan origin ip-address 192.168.1.2 global
+\end{verbatim}
+
+\subsection{openvswitch.ko}\label{ovs}
+Open vSwitch consists of a userspace daemon, ovs-vswitchd, and a kernel
+datapath implementation, openvswitch.ko.
+This example shows a case where we only use the netlink API and openvswitch.ko
+module, without the ovs-vswitchd daemon.
+ovs-dpctl is a stand-alone tool which programs openvswitch.ko
+through network api, see Joes' paper
+\begin{verbatim}
+ip link add dev myerspan type erspan external
+ovs-dpctl add-dp mydp
+ovs-dpctl add-if mydp myerspan
+ovs-dpctl add-if mydp veth1 // connected to VM1
+ovs-dpctl add-flow \
+    "in_port(2)" \  // any packets matching in_port=2
+    "set(tunnel(tun_id=20,dst=192.168.1.1,ttl=64,\
+    erspan(ver=2,dir=1,hwid=0x4),flags(df|key))),3"
+\end{verbatim}
+
+\subsection{eBPF and iproute2}\label{iproute2}
+
+Assuming we want to make a copy of all traffic from the physical
+device eth1, and encapsulate them through ERSPAN tunnel.
+We first create a native-mode ERSPAN tunnel using ip-link command,
+and make a copy of all traffic from eth1 to the ERSPAN tunnel netdev.
+%see net/ip6_gre_headroom.sh
+\begin{verbatim}
+ip link add dev myerspan type erspan seq key 30 \
+    local 192.168.1.4 remote 192.168.1.1 \
+    erspan_ver 1 erspan 123
+tc filter add dev eth1 ingress pref 1000 matchall skip_hw \
+    action mirred egress mirror dev myerspan
+\end{verbatim}
+
+For the eBPF tunnel cases,
+we create a metadata mode erspan tunnel, and set the
+remote ip and tunnel id to 30, attach the eBPF program,
+and create the fowarding rule using tc.
+\begin{verbatim}
+ip link add dev myerspan type erspan external
+tc qdisc add dev myerspan clsact
+tc filter add dev myerspan bpf da obj test_tunnel_kern.o section set_erspan
+tc filter add dev eth1 ingress pref 1000 matchall skip_hw \
+    action mirred egress mirror dev myerspan
 \end{verbatim}
@@
 \section{Conclusion}
+\section{Future Work}
 \section{Acknowledgments}
-\section{Future Work}
 

### 2018-10-15 paper.tex
work on section 3

@@
 a ERSPAN mirrored packet simply make a copy and forward to the ERSPAN netdev.
-For example, a physical netdev can use TC~\cite{tc} to copy a packet
-to the erspan tunnel~\cite{tcselftest}.
+For example, a physical netdev can use linux TC~\cite{tcsubsys} with mirror
+action to copy a packet to the erspan tunnel.
 
@@
 Any packet arriving at the ERSPAN tunnel netdev's receive queue will
-be decapsulated. Tools such as Wireshark~\cite{wireshark} can be used
-to inspect the mirrored packet.
+be decapsulated. Tools such as Wireshark~\cite{wireshark_erspan,wireshark_erspan2}
+can be used to inspect the mirrored packet.
 
@@
 \begin{verbatim}
-<------------ outer -------------->  <---- inner ----...
+<------------ outer -------------> <---- inner ---- ...
 +-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+-+
@@
 this is not scalable because every host in the network creates
-mutiple tunnels with different configurations to every other hosts~\cite{mvp}.
+mutiple tunnels with different configurations to every other hosts~\cite{nvp}.
 
@@
 in data center such as gateways.
-Assuming all the monitored servers are under IP subnet of $10.1.1.*$,
+Assuming all the monitored servers are under IP network of $10.1.1.*$,
 and We place a traffic sniifer over another IP network of $192.168.1.*$.
@@
 We use Nexus 5000 switch and configure its ERSPAN tunnel
-on ports 11 and 12 as below.
+with session ID 10, remote IP pointing to the traffic sniffer, $192.168.1.1$,
+and local IP address as $192.168.1.2$.  As a result, both the ingress and
+egress traffic on ports 11 and 12 will be mirrored to the remote sniffer.
 \begin{verbatim}
@@
 
-\subsection{openvswitch.ko}\label{ovs}
-Open vSwitch consists of a userspace daemon, ovs-vswitchd, and a kernel
-datapath implementation, openvswitch.ko.
-This example shows a case where we only use the netlink API and openvswitch.ko
-module, without the ovs-vswitchd daemon.
-ovs-dpctl is a stand-alone tool which programs openvswitch.ko
-through network api, see Joes' paper
+\subsection{Open vSwitch Kernel Module}\label{ovs}
+Open vSwitch consists of two components: a userspace daemon, called ovs-vswitchd,
+and a flow cache as a kernel module, called openvswitch.ko.  While ovs-vswitchd
+talks to the OpenFlow controller and programs its OpenFlow flow tables,
+the openvswitch.ko keeps a cache where the subsequent flows are handled
+inside the kernel space.
+
+The openvswitch.ko provides a user-facing netlink API that models a network
+bridge that connects multiple ports through a single table~\cite{ovswoovs}.
+This example shows how to use the netlink API provided by openvswitch.ko
+module, with the utility, ovs-dpctl, to create a ERSPAN tunnel.
 \begin{verbatim}
+# creating datapath named "mydp", attach veth1(port 2)
+ovs-dpctl add-dp mydp
+ovs-dpctl add-if mydp veth1 // connected to VM1
+
+# creating erspan dev named "myerspan" and attach
 ip link add dev myerspan type erspan external
-ovs-dpctl add-dp mydp
 ovs-dpctl add-if mydp myerspan
-ovs-dpctl add-if mydp veth1 // connected to VM1
+
+# flow entry for port 2 to erspan tunnel 
 ovs-dpctl add-flow \
@@
 \end{verbatim}
+
+%\begin{lstlisting}[caption={Example ovs-dpctl usage},language=bash,label=lst:dpctl,breaklines=true]
+%\end{lstlisting}
 

### 2018-10-15 paper.tex
finish section 3

@@
 | Physical |         |     VM1  VM2 ...  |      |     linux      |
-| Machines |         | 10.1.1.3  |       |      |    netdevs     |
+| Machines |         | 10.1.1.3  |       |      |   netdev,eth1  |
 +----------+         |  +--------------+ |      |      |         |
@@
 ovs-dpctl add-flow \
-    "in_port(2)" \  // any packets matching in_port=2
+    "in_port(2)" \
     "set(tunnel(tun_id=20,dst=192.168.1.1,ttl=64,\
@@
 
-%\begin{lstlisting}[caption={Example ovs-dpctl usage},language=bash,label=lst:dpctl,breaklines=true]
+%\begin{lstlisting}
+%[caption={Example ovs-dpctl usage},language=bash,label=lst:dpctl,breaklines=true]
 %\end{lstlisting}
 
-\subsection{eBPF and iproute2}\label{iproute2}
+\subsection{iproute2 with/without eBPF}\label{iproute2}
+Assuming we want to mirror all traffic from the physical device eth1
+to an ERSPAN tunnel with session ID 30, as shown in the right Figure~\ref{example},
+we first create a native-mode ERSPAN tunnel using ip-link command,
+and mirror traffic from eth1 to the ERSPAN tunnel netdev.
+For eBPF use case, instead of creating native-mode tunnel, we create
+a metadata-mode tunnel using the key word "external".
+Then, tc qdisc and filter rules are created for a eBPF program~\cite{daniel1,daniel2},
+"test\_tunnel\_kern.o" with section name "set\_erspan" to be executed,
+when receiving a packet from eth1 and sending through the "myerspan"
+tunnel device.
 
-Assuming we want to make a copy of all traffic from the physical
-device eth1, and encapsulate them through ERSPAN tunnel.
-We first create a native-mode ERSPAN tunnel using ip-link command,
-and make a copy of all traffic from eth1 to the ERSPAN tunnel netdev.
 %see net/ip6_gre_headroom.sh
 \begin{verbatim}
+# Native-mode without using eBPF
 ip link add dev myerspan type erspan seq key 30 \
@@
     erspan_ver 1 erspan 123
-tc filter add dev eth1 ingress pref 1000 matchall skip_hw \
-    action mirred egress mirror dev myerspan
+tc filter add dev eth1 ingress pref 1000 matchall \
+    skip_hw action mirred egress mirror dev myerspan
+
+# Metadata-mode with eBPF
+ip link add dev myerspan type erspan external
+tc qdisc add dev myerspan clsact
+tc filter add dev myerspan egress bpf direct-action \
+    obj test_tunnel_kern.o section erspan_set_tunnel
+tc filter add dev eth1 ingress pref 1000 matchall \
+    skip_hw action mirred egress mirror dev myerspan
 \end{verbatim}
 
-For the eBPF tunnel cases,
-we create a metadata mode erspan tunnel, and set the
-remote ip and tunnel id to 30, attach the eBPF program,
-and create the fowarding rule using tc.
+Note that for metadata-mode tunnel, the tunnel configuration is not
+provided from the ip route command line, but is passed in to the tunnel
+by the eBPF program, test\_tunnel\_kern.o. A code snippet creating this
+object from tools/testing/selftests/bpf/test\_tunnel\_kern.c is shown below.
+{\scriptsize
 \begin{verbatim}
-ip link add dev myerspan type erspan external
-tc qdisc add dev myerspan clsact
-tc filter add dev myerspan bpf da obj test_tunnel_kern.o section set_erspan
-tc filter add dev eth1 ingress pref 1000 matchall skip_hw \
-    action mirred egress mirror dev myerspan
+SEC("erspan_set_tunnel")
+int _erspan_set_tunnel(struct __sk_buff *skb)
+{
+        struct bpf_tunnel_key key;
+        struct erspan_metadata md; 
+        int ret;
+
+        __builtin_memset(&key, 0x0, sizeof(key));
+        key.remote_ipv4 = 0xc0a80101; /* 192.168.1.100 */
+        key.tunnel_id = 30; // session ID
+        key.tunnel_tos = 0;
+        key.tunnel_ttl = 64;
+
+        ret = bpf_skb_set_tunnel_key(skb, &key, sizeof(key),
+                                     BPF_F_ZERO_CSUM_TX);
+        if (ret < 0) {
+                ERROR(ret);
+                return TC_ACT_SHOT;
+        }
+
+        __builtin_memset(&md, 0, sizeof(md));
+        md.version = 1;
+        md.u.index = bpf_htonl(123);
+
+        ret = bpf_skb_set_tunnel_opt(skb, &md, sizeof(md));
+        if (ret < 0) {
+                ERROR(ret);
+                return TC_ACT_SHOT;
+        }
+
+        return TC_ACT_OK;
+}
 \end{verbatim}
-
-\section{Conclusion}
-\section{Future Work}
+}
+\section{Conclusion and Future Work}
+\mycomment{
 \section{Acknowledgments}
-
+The authors would like to acknowledge Justin Pettit for his guidance on writing
+this paper, Martynas Pumputis for providing context around WeaveNet, and Ben
+Pfaff, Hannes Sowa and Yingying Ren for providing review feedback.
+\section{Author Biography}
+Joe Stringer is a software engineer interested in networks and related fields,
+in particular SDN. He is actively engaged in the open-source community on
+network software projects including Open vSwitch and the Linux networking
+stack.
+}
 \bibliography{paper.bib}

### 2018-10-16 paper.tex
fix Greg's comments

@@
 \vspace{-0.5em}
-\caption{Overview of the ERSPAN tunnel use cases. ERSPAN tunnel can be
-created between }
+\caption{Overview of the ERSPAN tunnel use cases. ERSPAN tunnels can be
+created from a sniffer machine to Cisco switches, a Linux machine with
+multiple VMs, or simply a Linux machine.}
 \label{overview}
@@
 the software switch and remote traffic sniffer.
-Here, Open vSwitch~\cite{ovs} is an example capabale of creating filters
+Here, Open vSwitch~\cite{ovs} is an example capable of creating filters
 and forward packets to ERSPAN tunnels. More detailed configurations of
-Open vSwitch is described in later section.
+Open vSwitch are described in later section.
 
@@
 Mirrored traffic arrives at the sniffer machine needs to be able to
-extract and restore the original monitored frame.  To differentiated
+extract and restore the original monitored frame.  To differentiate
 the three use cases, the administrator can create three ERSPAN session
@@
 \caption{An example of mirrored packet with outer header containing
-the GRE and ERSPAN header, followed by the innter Ethernet frame.}
+the GRE and ERSPAN header, followed by the inner Ethernet frame.}
 \label{erspanhdr}
@@
 In this section we describe the basic ERSPAN protocol header format
-along with its implementation to Linux kernel.
+along with its implementation in the Linux kernel.
 For IPv4/IPv6, the implementation is under net/ipv4/ip\_gre.c and
@@
 
-\subsection{Native v.s Metadata-Mode Tunnel}
+\subsection{Native vs Metadata-Mode Tunnel}
 %https://netdevconf.org/1.2/papers/borkmann.pdf

### 2018-10-16 paper.tex
conclusion

@@
-\documentclass{sigplanconf}
+\documentclass[10pt]{sigplanconf}
 
@@
 Currently there are two ways of using metadata-mode tunnel, one through
-OVS and the other through eBPF~\cite{dborkman}.
+OVS and the other through eBPF~\cite{daniel2}.
 We implement both the native mode and metadata-mode~\cite{erspanmd}
@@
 }
-\section{Conclusion and Future Work}
+\section{Conclusion}
+Port mirroring is the most common troubleshooting techniques
+allowing a user to send a copy of the monitored traffic to a packet analyzer.
+ERSPAN extends its precedence SPAN and RSPAN, by allowing the monitored
+traffic to route across IP networks.
+In this paper, we describe the implementation of ERSPAN and demonstrate three
+ways to use the ERSPAN protocol in Linux, by creating a native-mode ERSPAN tunnel
+, or by creating eBPF byte-code with metadata-mode tunnel, or by using Open
+vSwitch kernel module. 
+We'd like to thank many people for giving review comments feedbacks for our
+ERSPAN patches.
+
 \mycomment{

### 2018-10-18 paper.tex
minor fixes
wip: add openvswitch impl section

@@
 properly.  The truncate bit is detected by comparing the the mirrored frame's
-skb->len and the length its IP header reports~\cite{erspantruncate}.
+\texttt{skb->len} and the length its IP header reports.
 %commit: erspan: auto detect truncated packets.
@@
 
+\mycomment{
+\subsection{Open vSwitch Kernel Module}
+%configuration
+Similar to other tunnel types such as VxLAN and Geneve,
+Open vSwitch kernel module, openvswitch.ko, configures the Linux
+ERSPAN tunnel by getting the binary tunnel configuration blob from
+its userspace daemon, ovs-vswitchd, verifies its parameters, and
+copies the tunnel data into flow key (struct sw\_flow\_key).
+As a result, the tunnel configuration is per-flow key set-up.
+
+When OVS kernel module process 
+% struct ip_tunnel_info
+
+% describe how OVS uses it
+% /net/openvswitch/flow_netlink.c
+commit fc1372f89ffe1f58b589643b75f679e452350703
+Author: William Tu <u9012063@gmail.com>
+Date:   Thu Jan 25 13:20:11 2018 -0800
+
+    openvswitch: add erspan version I and II support
+
+    The patch adds support for openvswitch to configure erspan
+ %   v1 and v2.  The OVS_TUNNEL_KEY_ATTR_ERSPAN_OPTS attr is added
+    to uapi as a binary blob to support all ERSPAN v1 and v2's
+    fields.  Note that Previous commit "openvswitch: Add erspan tunnel
+    support." was reverted since it does not design properly.
+
+}
 \section{Example Use Case}

### 2018-10-22 paper.tex
fix comments from greg

@@
 The implementation includes both transmission and reception and is based on the
-existing ip\_gre and ip6\_gre kernel module.  As a result, Linux today can act as
+existing ip\_gre and ip6\_gre kernel modules.  As a result, Linux today can act as
 an ERSPAN traffic source sending the ERSPAN mirrored traffic to the remote host,
@@
 inside a Linux box, the virtual switch forwarding the packet between
-virtual and physical network can also create ERSPAN tunnels between
+virtual and physical networks can also create ERSPAN tunnels between
 the software switch and remote traffic sniffer.
 Here, Open vSwitch~\cite{ovs} is an example capable of creating filters
-and forward packets to ERSPAN tunnels. More detailed configurations of
+and forwarding packets to ERSPAN tunnels. More detailed configurations of
 Open vSwitch are described in later section.
@@
 As a result on the right-most, any other linux netdev which wants to create
-a ERSPAN mirrored packet simply make a copy and forward to the ERSPAN netdev.
+a ERSPAN mirrored packet simply makes a copy and forwards to the ERSPAN netdev.
 For example, a physical netdev can use linux TC~\cite{tcsubsys} with mirror
@@
 
-Mirrored traffic arrives at the sniffer machine needs to be able to
+Mirrored traffic arriving at the sniffer machine needs to be able to
 extract and restore the original monitored frame.  To differentiate
 the three use cases, the administrator can create three ERSPAN session
-ID, a configuration parameter for grouping the mirrored traffic.
-For Linux user, an ERSPAN tunnel can also be used at the sniffer size.
+IDs, a configuration parameter for grouping the mirrored traffic.
+For Linux users, an ERSPAN tunnel can also be used at the sniffer side.
 Any packet arriving at the ERSPAN tunnel netdev's receive queue will
@@
 
-ERSPAN protocol was developed by Cisco and its specification is published at IETF
+The ERSPAN protocol was developed by Cisco and its specification is published at IETF
 draft~\cite{erspan_ietf}. 
 Figure~\ref{erspanhdr} shows an example of ERSPAN encapsulated
-packet, with outer header consists of Ethernet header, followed by IPv4/IPv6
-header, followed by a fixed 8-byte GRE header, and followed by ERSPAN header.
+packet, with outer header consisting of Ethernet header, following by IPv4/IPv6
+header, following by a fixed 8-byte GRE header, and following by ERSPAN header.
 After the ERSPAN header, the inner frame is followed so that the ERSPAN receiver
@@
 ERSPAN type III, the GRE's next protocol type is 0x22EB with 12-byte ERSPAN header
-size, if no optinal subheader enabled.
+size, if no optional subheader enabled.
 
@@
 frame has been truncated.
-Session ID is a 10-bit field as an identification of each ERSPAN mirring
+Session ID is a 10-bit field as an identification of each ERSPAN mirroring
 session.
@@
 Index is also configurable by users through iproute2.
-The COS field and VLAN field are extrated from the original frame and set
+The COS field and VLAN field are extracted from the original frame and set
 properly.  The truncate bit is detected by comparing the the mirrored frame's
@@
 the frame payload has CRC error, too short, or too large~\cite{bso}.
-Timestamp is a 4-byte fields and can be configured with different granularities
+Timestamp is a 4-byte field and can be configured with different granularities
 (100 microseconds, 100 nanosecond, or IEEE1588) at the Gra field.
@@
 802.3 frame, or a IP packet.
-Hardware ID, Hw ID, is an unique identifier of an ERSPAN engine
+Hardware ID, Hw ID, is an unique identifier of an ERSPAN engine,
 Direction bit, D, indicates whether the original frame was
 SPAN'ed in ingress(0) or in egress(1).
-Finally, O indicates whether or not the optinal platform-specific
+Finally, O indicates whether or not the optional platform-specific
 subheader is presented.
@@
 \texttt{ktime\_get\_real()} with 100 microseconds granularity.
-Currently we do not support other timer granulartiy.
+Currently we do not support other timer granularties.
 In addition, the SGT is hard-coded to 0, non-ethernet mirrored packet
@@
 the three configuration ways of ERSPAN.
-Assuming a network administrator wants to monitor a network consists
+Assuming a network administrator wants to monitor a network consisting
 of 1) physical machines connected to Cisco switches, 2)
@@
 \section{Conclusion}
-Port mirroring is the most common troubleshooting techniques
+Port mirroring is the most common troubleshooting technique
 allowing a user to send a copy of the monitored traffic to a packet analyzer.
-ERSPAN extends its precedence SPAN and RSPAN, by allowing the monitored
+ERSPAN extends its precedences, SPAN and RSPAN, by allowing the monitored
 traffic to route across IP networks.

### 2018-11-05 paper.tex
revise figure

@@
 
-Metada-mode tunnel, or light weight tunnel, is designed for solving
+Metadata-mode tunnel, or called light-weight tunnel, is designed for solving
 the limitation.  The fundamental idea is that only one netdev per
@@
 and local IP address as $192.168.1.2$.  As a result, both the ingress and
-egress traffic on ports 11 and 12 will be mirrored to the remote sniffer.
+egress traffic on ports 11 and 12 will be msdfirrored to the remote sniffer.
+{\footnotesize
 \begin{verbatim}
@@
 \end{verbatim}
+}
 
@@
 module, with the utility, ovs-dpctl, to create a ERSPAN tunnel.
+
+{\footnotesize
 \begin{verbatim}
@@
 \end{verbatim}
-
+}
 %\begin{lstlisting}
@@
 %see net/ip6_gre_headroom.sh
+
+{\footnotesize
 \begin{verbatim}
@@
 \end{verbatim}
-
+}
 Note that for metadata-mode tunnel, the tunnel configuration is not
@@
 object from tools/testing/selftests/bpf/test\_tunnel\_kern.c is shown below.
-{\scriptsize
+{\footnotesize
 \begin{verbatim}

### 2018-11-05 paper.tex
fix tc use cases

@@
 # creating erspan dev named "myerspan" and attach
+# lightweight tunnel is used with "external" keyword
 ip link add dev myerspan type erspan external
@@
 
-# flow entry for port 2 to erspan tunnel 
+# flow entry for port 1 to erspan tunnel port 3 
 ovs-dpctl add-flow \
-    "in_port(2)" \
+  "in_port(1),eth(src=00:01:02:03:04:05,dst=10:11:12:13:14:15),\
+  eth_type(0x0800),ipv4(src=35.8.2.41,dst=172.16.0.20,proto=5,\
+  tos=0x80,ttl=128,frag=no)" \
   "set(tunnel(tun_id=20,dst=192.168.1.1,ttl=64,\
   erspan(ver=2,dir=1,hwid=0x4),flags(df|key))),3"
+
+ovs-dpctl dump-flows
 \end{verbatim}
@@
     erspan_ver 1 erspan 123
-tc filter add dev eth1 ingress pref 1000 matchall \
+
+# eth1 is the mirrored device
+tc qdisc add dev eth1 handle ffff: ingress
+tc filter add dev eth1 handle ffff: ingress matchall \
     skip_hw action mirred egress mirror dev myerspan
@@
     obj test_tunnel_kern.o section erspan_set_tunnel
-tc filter add dev eth1 ingress pref 1000 matchall \
+
+tc qdisc add dev eth1 handle ffff: ingress
+tc filter add dev eth1 parent ffff: matchall \
     skip_hw action mirred egress mirror dev myerspan
